---
title: "Bradypus"
author: "Brad Anderson"
date: "October 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(dismo)
library(tidyverse)
library(sf)
library(sp)
library(raster)
library(rgdal)
library(maptools)


```

```{r PARAMETERS and FILE LOCATIONS}

```


#Import species occurence points.
```{r species points}

#oakwoodland_points <- shapefile(G:/Working_Maps/Brad/ESM270P/oakwoodland_points.shp)
#oakwoodland_points

oak_points <- read_csv("~/github/sdm/oakwoodland_points.csv")
head(oak_points)

#Plot Points
data(wrld_simpl)
plot(wrld_simpl, xlim=c(-121,-120), ylim=c(34,35), axes=TRUE, col="light yellow")
points(oak_points$Long, oak_points$Lat, col='red', cex=0.75)


```

#Import environmental data:
"For any particular study the layers should all have the same spatial extent, resolution, origin, and projection. If necessary, use functions like crop, extend, aggregate, resample, and projectRaster from the raster package."

```{r environmental data}
var_path <- file.path("H:/SDM/CCMSM4_rcp85/2010-2039/")
r1 <- raster("H:/SDM/CCMSM4_rcp85/2010-2039/aet2010_2039_ave_CCSM4_rcp85_1539579674.tif")
plot(r1)

```

```{r create raster stack of envi variables}

variables <- list.files(var_path, pattern='tif$', full.names=TRUE )
variables

#predictors <- stack(variables)
#predictors
#names(predictors)
#plot(predictors)

```

Questions:
How do I import a shapefile? -I exported a comma delimited .txt file from Arc Pro and then turned into a .csv before importing into RStudio.
Should I do a different model run for each forecast time period? (ie 2010-2039,2040-2069,2070-2099)
Extent - run it across the whole state and then crop the preserve?
