---
title: "Bradypus"
author: "Brad Anderson"
date: "October 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(dismo)
library(tidyverse)
library(sf)
library(sp)
library(raster)
library(rgdal)
library(maptools)


```

```{r PARAMETERS and FILE LOCATIONS}

#Species Occurence Points
points <- read_csv("~/github/sdm/oakwoodland_points.csv")

#Environmental Variables Folder
variable_path <- file.path("H:/SDM/CCMSM4_rcp85/2010-2039/")

```

Alternatively, could I draw the points out of a shapefile?
```{r}

#oakwoodland_points <- shapefile("H:/SDM/OccurencePoints/OakWoodland_points_Project.shp")
#oakwoodland_points

```


#Import species occurence points.
```{r plot points}

#Plot Points
data(wrld_simpl)
plot(wrld_simpl, xlim=c(-121,-120), ylim=c(34,35), axes=TRUE, col="light yellow")
points(points$Long, points$Lat, col='red', cex=0.75)


```

#Import environmental data:
"For any particular study the layers should all have the same spatial extent, resolution, origin, and projection. If necessary, use functions like crop, extend, aggregate, resample, and projectRaster from the raster package."

```{r create raster stack of envi variables}

variables <- list.files(variable_path, pattern='tif$', full.names=TRUE )
variables

predictors <- stack(variables)
predictors
names(predictors)
plot(predictors)

```

Questions:
How do I import a shapefile? -I exported a comma delimited .txt file from Arc Pro and then turned into a .csv before importing into RStudio.

Should I do a different model run for each forecast time period? (ie 2010-2039,2040-2069,2070-2099)

Extent - run it across the whole state and then crop the preserve? Start with the preserve.

Where I left off: checking the projections of the raster layers, they show as NA...
