Please find below the R code history from your *Wallace* v1.0.6.1 session.

You can reproduce your session results by running this R Markdown file in RStudio.

Each code block is called a "chunk", and you can run them either one-by-one or all at once by choosing an option in the "Run" menu at the top-right corner of the "Source" pane in RStudio.

For more detailed information see <http://rmarkdown.rstudio.com>).

### Package installation

Wallace uses the following R packages that must be installed and loaded before starting.

```{r}
library(spocc)
library(spThin)
library(dismo)
library(rgeos)
library(ENMeval)
library(dplyr)
```

Wallace also includes several functions developed to help integrate different packages and some additional functionality. For this reason, it is necessary to load the file `functions.R`, The function `system.file()` finds this script, and `source()` loads it.

```{r}
source(system.file('shiny/funcs', 'functions.R', package = 'wallace'))
```

Record of analysis for \*\*.
----------------------------

User CSV path with occurrence data. If the CSV file is not in the current workspace, change to the correct file path (e.g. "/Users/darwin/Documents/occs.csv").

```{r}
# NOTE: provide the path to the folder that contains the CSV file
d.occs <- ''
# create path to user occurrences csv file
userOccs.path <- file.path(d.occs, "oakwoodland_points.csv")
# read in csv
userOccs.csv <- read.csv(userOccs.path, header = TRUE)
# remove rows with duplicate coordinates
occs.dups <- duplicated(userOccs.csv[c('longitude', 'latitude')])
occs <- userOccs.csv[!occs.dups,]
# remove NAs
occs <- occs[complete.cases(occs$longitude, occs$latitude), ]
# give all records a unique ID
occs$occID <- row.names(occs)
```

### Process Occurrence Data

The following code recreates the polygon used to select occurrences to keep in the analysis.

```{r}
selCoords <- data.frame(x = c(-120.5523, -120.5591, -120.3689, -120.3353, -120.5523), y = c(34.4324, 34.5925, 34.5852, 34.4245, 34.4324))
selPoly <- sp::SpatialPolygons(list(sp::Polygons(list(sp::Polygon(selCoords)), ID=1)))
occs.xy <- occs[c('longitude', 'latitude')]
sp::coordinates(occs.xy) <- ~ longitude + latitude
intersect <- sp::over(occs.xy, selPoly)
intersect.rowNums <- as.numeric(which(!(is.na(intersect))))
occs <- occs[intersect.rowNums, ]
```

### Obtain Environmental Data

Using WorldClim (<http://www.worldclim.org/>) bioclimatic dataset at resolution of 0.5 arcmin.

```{r}
# get WorldClim bioclimatic variable rasters
envs <- raster::getData(name = "worldclim", var = "bio", res = 0.5, lat = 34.52, lon = -120.425)
# change names rasters variables
envRes <- 0.5
if (envRes == 0.5) {
  i <- grep('_', names(envs))
  editNames <- sapply(strsplit(names(envs)[i], '_'), function(x) x[1])
  names(envs)[i] <- editNames
}
i <- grep('bio[0-9]$', names(envs))
editNames <- paste('bio', sapply(strsplit(names(envs)[i], 'bio'), function(x) x[2]), sep='0')
names(envs)[i] <- editNames
# subset by those variables selected
envs <- envs[[c('bio01', 'bio02', 'bio03', 'bio04', 'bio05', 'bio06', 'bio07', 'bio08', 'bio09', 'bio10', 'bio11', 'bio12', 'bio13', 'bio14', 'bio15', 'bio16', 'bio17', 'bio18', 'bio19')]]
# extract environmental values at occ grid cells
locs.vals <- raster::extract(envs[[1]], occs[, c('longitude', 'latitude')])
# remove occs without environmental values
occs <- occs[!is.na(locs.vals), ]  
```

### Process Environmental Data

Background selection technique chosen as Minimum Convex Polygon.

```{r}
occs.xy <- occs[c('longitude', 'latitude')]
sp::coordinates(occs.xy) <- ~ longitude + latitude
bgExt <- mcp(occs.xy)
```

Buffer size of the study extent polygon defined as 0.5 degrees.

```{r}
bgExt <- rgeos::gBuffer(bgExt, width = 0.5)
```

Mask environmental variables by Minimum Convex Polygon, and take a random sample of background values from the study extent. As the sample is random, your results may be different than those in the session. If there seems to be too much variability in these background samples, try increasing the number from 10,000 to something higher (e.g. 50,000 or 100,000). The better your background sample, the less variability you'll have between runs.

```{r}
# crop the environmental rasters by the background extent shape
envsBgCrop <- raster::crop(envs, bgExt)
# mask the background extent shape from the cropped raster
envsBgMsk <- raster::mask(envsBgCrop, bgExt)
# sample random background points
bg.xy <- dismo::randomPoints(envsBgMsk, 10000)
# convert matrix output to data frame
bg.xy <- as.data.frame(bg.xy)  
```

### Partition Occurrence Data

Occurrence data is now partitioned for cross-validation, a method that iteratively builds a model on all but one group and evaluates that model on the left-out group.

For example, if the data is partitioned into 3 groups A, B, and C, a model is first built with groups A and B and is evaluated on C. This is repeated by building a model with B and C and evaluating on A, and so on until all combinations are done.

Cross-validation operates under the assumption that the groups are independent of each other, which may or may not be a safe assumption for your dataset. Spatial partitioning is one way to ensure more independence between groups.

You selected to partition your occurrence data by the method.

```{r}
occs.xy <- occs[c('longitude', 'latitude')]
group.data <- ENMeval::get.randomkfold(occ=occs.xy, bg.coords=bg.xy, kfolds=4)
```

```{r}
# pull out the occurrence and background partition group numbers from the list
occs.grp <- group.data[[1]]
bg.grp <- group.data[[2]]
```

### Build and Evaluate Niche Model

You selected the maxent model.

```{r}
# define the vector of regularization multipliers to test
rms <- seq(1, 3, 1)
# iterate model building over all chosen parameter settings
e <- ENMeval::ENMevaluate(occs.xy, envsBgMsk, bg.coords = bg.xy, RMvalues = rms, fc = c('H', 'LQH'), 
                          method = 'user', occs.grp, bg.grp, clamp = TRUE, algorithm = "maxent.jar")

# unpack the results data frame, the list of models, and the RasterStack of raw predictions
evalTbl <- e@results
evalMods <- e@models
names(evalMods) <- e@results$settings
evalPreds <- e@predictions
```

```{r}
# view ENMeval results
ENMeval::eval.plot(evalTbl, value = "avg.test.AUC")
```
